Memory-efficient Mixed-Precision Implementations for\\Robust Explicit MPC

### 2019-04-07 emsoft-2019/main.tex
First draft of tables; Removed fake authors
DOuble blind

%
% The first command in your LaTeX source must be the \documentclass command.
\documentclass[sigconf,review,anonymous]{acmart}
\usepackage{listings}
\usepackage{multirow}
\usepackage{lscape}
\usepackage{amsmath}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows}
\usepackage{graphicx}

\newcommand{\statevar}{x_{k}}
\newcommand{\statevarmath}{$x_{k}\,$}
\newcommand{\qstatevar}{\hat{x}_{k}}
\newcommand{\qstatevarmath}{$\hat{x}_{k}\,$}
\newcommand{\statespace}{X}
\newcommand{\regioni}[1]{$X_{{#1}}$}
\newcommand{\regionimath}[1]{X_{{#1}}}
% Rights management information. 
% This information is sent to you when you complete the rights form.
% These commands have SAMPLE values in them; it is your responsibility as an author to replace
% the commands and values with those provided to you when you complete the rights form.
%
% These commands are for a PROCEEDINGS abstract or paper.
% \copyrightyear{2018}
% \acmYear{2018}
% \setcopyright{acmlicensed}
% \acmConference[Woodstock '18]{Woodstock '18: ACM Symposium on Neural Gaze Detection}{June 03--05, 2018}{Woodstock, NY}
% \acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection, June 03--05, 2018, Woodstock, NY}
% \acmPrice{15.00}
% \acmDOI{10.1145/1122445.1122456}
% \acmISBN{978-1-4503-9999-9/18/06}

@@

%
% The "author" command and its associated commands are used to define the authors and their affiliations.
% Of note is the shared affiliation of the first two authors, and the "authornote" and "authornotemark" commands
% used to denote shared contribution to the research.

% \author{Ben Trovato}
% \authornote{Both authors contributed equally to this research.}
% \email{trovato@corporation.com}
% \orcid{1234-5678-9012}
% \author{G.K.M. Tobin}
% \authornotemark[1]
% \email{webmaster@marysville-ohio.com}
% \affiliation{%
%   \institution{Institute for Clarity in Documentation}
%   \streetaddress{P.O. Box 1212}
%   \city{Dublin}
%   \state{Ohio}
%   \postcode{43017-6221}
% }

@@

@@

\input{intro}
\input{motiv}
\input{RMPC_Daisy}
\input{Methodology}
\input{experiments}
\input{Conclusion}

>>>>

%
% The first command in your LaTeX source must be the \documentclass command.
\documentclass[sigconf,review,anonymous,dvipsnames]{acmart}
\usepackage{listings}
\usepackage{multirow}
\usepackage{lscape}
\usepackage{amsmath}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows}
\usepackage{graphicx}
\usepackage[T1]{fontenc} 
\usepackage[scaled=0.80]{beramono}
\usepackage{graphicx} % http://ctan.org/pkg/graphicx
\usepackage{booktabs} % http://ctan.org/pkg/booktabs
\usepackage{xparse}
\setlength{\tabcolsep}{0.5em} % for the horizontal padding
{\renewcommand{\arraystretch}{1.1}% for the vertical padding
%\usepackage[dvipsnames]{xcolor}
\usepackage[backgroundcolor=Apricot, textsize=footnotesize]{todonotes}
\newcommand*{\eva}[1]{\todo[author=Eva,inline,caption={}]{#1}}

\newcommand{\statevar}{x_{k}}
\newcommand{\statevarmath}{$x_{k}\,$}
\newcommand{\qstatevar}{\hat{x}_{k}}
\newcommand{\qstatevarmath}{$\hat{x}_{k}\,$}
\newcommand{\statespace}{X}
\newcommand{\regioni}[1]{$X_{{#1}}$}
\newcommand{\regionimath}[1]{X_{{#1}}}
\newcommand{\maxUij}{$max|U_{i}-U_{j}|$}
% Rights management information. 
% This information is sent to you when you complete the rights form.
% These commands have SAMPLE values in them; it is your responsibility as an author to replace
% the commands and values with those provided to you when you complete the rights form.
%
% These commands are for a PROCEEDINGS abstract or paper.
% \copyrightyear{2018}
% \acmYear{2018}
% \setcopyright{acmlicensed}
% \acmConference[Woodstock '18]{Woodstock '18: ACM Symposium on Neural Gaze Detection}{June 03--05, 2018}{Woodstock, NY}
% \acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection, June 03--05, 2018, Woodstock, NY}
% \acmPrice{15.00}
% \acmDOI{10.1145/1122445.1122456}
% \acmISBN{978-1-4503-9999-9/18/06}

@@

%
% The "author" command and its associated commands are used to define the authors and their affiliations.
% Of note is the shared affiliation of the first two authors, and the "authornote" and "authornotemark" commands
% used to denote shared contribution to the research.
%\author{Ben Trovato}
%\authornote{Both authors contributed equally to this research.}
%\email{trovato@corporation.com}
%\orcid{1234-5678-9012}
%\author{G.K.M. Tobin}
%\authornotemark[1]
%\email{webmaster@marysville-ohio.com}
%\affiliation{%
%  \institution{Institute for Clarity in Documentation}
%  \streetaddress{P.O. Box 1212}
%  \city{Dublin}
%  \state{Ohio}
%  \postcode{43017-6221}
%}

%\author{Lars Th{\o}rv{\"a}ld}
%\affiliation{%
%  \institution{The Th{\o}rv{\"a}ld Group}
%  \streetaddress{1 Th{\o}rv{\"a}ld Circle}
%  \city{Hekla}
%  \country{Iceland}}
%\email{larst@affiliation.org}

%\author{Valerie B\'eranger}
%\affiliation{%
%  \institution{Inria Paris-Rocquencourt}
%  \city{Rocquencourt}
%  \country{France}
%}

%\author{Aparna Patel}
%\affiliation{%
% \institution{Rajiv Gandhi University}
% \streetaddress{Rono-Hills}
% \city{Doimukh}
% \state{Arunachal Pradesh}
% \country{India}}

@@

\renewcommand{\shortauthors}{}

@@

\input{intro}
\input{Motiv}
\input{RMPC_Daisy}
\section{Error Analysis}
\eva{Assuming a given precision, how to compute the error for a given controller}
\section{Controller Synthesis}
\eva{How we actually get the controller, including feedback loop and mixed-precision tuning}
\input{Methodology}
\input{experiments}
\input{related}
\input{conclusion}
